\chapter{User Study Survey} \label{appendix:survey}

\section{Demographic Questions} 
The survey starts with some demographic questions to allow statements about the sampled population.
\\ \\
\textbf{Question} What is your primary profession? \\
\textbf{Answer} Text field. \\ \\
\textbf{Question} How old are you? \\
\textbf{Answer} Text field.

\section{The Post-Study Questionnaire} 
The participants are given the questionnaire after they have completed all the scenarios in the user study.
\subsection{Likert Scale Statements}
In this section, participants need to indicate their rate of approval on a 1-5 point Likert (discrete) scale. The Likert scales are anchored at the end points with the terms "Strongly disagree" for 1 and "Strongly agree" for 5. Questions are asked separately for the two tested variants.
\\ \\
\textbf{Context-Aware System} \\
\textbf{Q1}: It was easy to find the information I needed. \\
\textbf{Q2}: The system is effective in helping me to complete the scenario. \\
\textbf{Q3}: I like using this system. \\
\textbf{Q4}: I understood the benefit of using the contextual conditions.  \\
\textbf{Q5}: I am satisfied with the provided contextual explanations.  \\
\textbf{Q6}: I believe that the contextual explanations are useful. \\
\textbf{Q7}: The contextual explanations provided by this system are clear.  \\
\\ \\
\textbf{Non-Context-Aware System} \\
\textbf{Q8}: It was easy to find the information I needed.  \\
\textbf{Q9}: The system is effective in helping me to complete the scenario.  \\
\textbf{Q10}: I like using this system.

\subsection{Regular Questions} 
In this section, participants need to choose between two candidate options: a. Context-aware recommender system b. Non-context-aware recommender system
\\ \\
\textbf{Q11}: Which system do you prefer? \\
\textbf{Q12}: Which system suggest more appropriate clothes? \\


